### 2021-10-12 paper/pldi22/abstract.tex
Minor update in abstract

  To alleviate this problem, we present $\tool$, a \textit{live} language design
  assistant for JavaScript. It automatically synchronizes with a given language
  specification and shows related conformance tests in the revision process.
  Moreover, to better comprehend language semantics, we present a way to focus
  on specific semantics by automatically reducing semantics and filtering out
  conformance tests with user-defined \textit{syntactic views}. In this paper,
  we conduct several case studies for JEDIT to demonstrate the effectiveness of
  live language design with syntactic views. Moreover, we experimentally show
  that syntactic views successfully reduce the \inred{XX.X}\% of semantics and
  filter out \inred{XX.X}\% of conformance tests on average using historically
  representative syntactic views.
\end{abstract}

>>>>

  To alleviate this problem, we present $\tool$, a \textit{live} language design
  assistant for JavaScript. It automatically synchronizes with a given language
  specification and shows related conformance tests in the revision process.
  Moreover, to better comprehend language semantics, we present a way to focus
  on specific semantics by automatically reducing semantics and filtering out
  conformance tests using user-defined \textit{syntactic views}, abstract syntax
  trees with abstracted nodes. In this paper, we conduct several case studies
  for JEDIT to demonstrate the effectiveness of live language design with
  syntactic views. Moreover, we experimentally show that syntactic views
  successfully reduce the \inred{XX.X}\% of semantics and filter out
  \inred{XX.X}\% of conformance tests on average using \inred{historically
  representative syntactic views}.
\end{abstract}
